\vspace{1.0cm} \Large \bf Supplemental material of ``Health and disease imprinted in the time variability of the human microbiome''

### 2016-12-07 mSystems/mSys_suppl.tex
Minor changes to mSys_MAIN to adapt to mSystems' staff requirements
On branch master
	modified:   mSys_MAIN.pdf
	modified:   mSys_MAIN.tex
	modified:   mSys_suppl.pdf
	modified:   mSys_suppl.tex
More minor changes
	modified:   ../mSys_MAIN.pdf
	modified:   ../mSys_MAIN.tex
	modified:   ../mSys_suppl.pdf
	modified:   ../mSys_suppl.tex
	modified:   Response to Reviewer Comments.docx
	modified:   mSys_MAIN_rev_marked.docx

% release codenumber (update it here!)
\newcommand\releasecode{initial}

@@

% watermarks (time consuming!)
\newwatermark[allpages,color=Purple!4,angle=45,scale=7,xpos=-40,ypos=0]{submitted}
\newwatermark[allpages,color=Purple!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript \releasecode\ submission}

>>>>

% release codenumber (update it here!)
\newcommand\releasecode{final}

@@

% watermarks (time consuming!)
\newwatermark[allpages,color=PineGreen!4,angle=45,scale=7,xpos=-40,ypos=0]{submitted}
\newwatermark[allpages,color=PineGreen!12,angle=0,scale=1,xpos=0,ypos=137]{
\emph{mSystems} \LaTeX\ manuscript \releasecode\ submission}
